\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/introduction.tex
something

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status, limiting
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns such as buttons and links on victim
computers by disguising \ac{USB} devices, e.g., mice.  This explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the host network usage.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a more extensive range of
peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.x.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a \ac{GUI} for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing works of \ac{USB} security from the aspects of attacking and
defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

>>>>

Despite the advantageous features of BadUSB, there exist several limitations as
follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
capabilities of BadUSB attacks.  When performing attacks on another host, the
attackers cannot obtain the current \ac{UI} status, limiting
them from taking subsequent moves.  For example, it is hard for attackers to
locate specific functional \ac{UI} patterns such as buttons and links on victim's
computers by disguising \ac{USB} devices, e.g., mice.  This explains why typical
BadUSB attacks often only stay in the command line, using commands to download
malicious scripts for execution.  However, these attacks may be intercepted by
anti-virus software or firewall due to the host network usage.  (2) To
our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
transmission rate for data and the support towards a more extensive range of
peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
can become more effective with the help of newly supported features in \ac{USB} 3.x.
(3) There have emerged multiple efficacious countermeasures after the
appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
It provides a \ac{GUI} for users to describe the functionalities or
roles of the \ac{USB} device and reject any usage beyond the description.
%\shuqing{Can't bypass USBCheckIn.}

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing works of \ac{USB} security from the aspects of attacking and
defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments we conducted are featured in
Section~\ref{sec:experiment}.  We present some possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

### 2021-03-22 WOOT/Files/related_work.tex
something

%Attacks against USB kernel drivers 
From the kernel perspective, its \ac{USB} software stack generally expects devices
to follow the \ac{USB} standard and may not consider corner cases of malformed \ac{USB}
packets. Based on this, Facedancer~\cite{facedancer} and
Syzkaller~\cite{syzkaller} use fuzzing techniques to uncover the bugs lying in
the kernel drivers. These bugs can cause kernel crashes and lead to a \ac{DoS} attack.
Though this poses a great challenge to the availability of a system, this
attack still requires physical access to the host and is unable to cause more
damage other than \ac{DoS}.

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they are using the victim's device. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitations compared with \tool: 
(1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
(2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.

>>>>

%Attacks against USB kernel drivers 
From the kernel perspective, its \ac{USB} software stack generally expects devices
to follow the \ac{USB} standard and may not consider corner cases of malformed \ac{USB}
packets. Based on this, Facedancer~\cite{facedancer} and
Syzkaller~\cite{syzkaller} use fuzzing techniques to uncover the bugs lying in
the kernel drivers. These bugs can cause kernel crashes and lead to a \ac{DoS} attack.
Though this poses a great challenge to the availability of a system, this
attack still requires physical access to the victim's device and is unable to cause more
damage other than \ac{DoS}.

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
victim's device, they could be recognized as a keyboard or mouse. Then attackers can
execute malicious payloads as they are using the victim's device. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim's device
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.

\ac{MHL} extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
\ac{JFA}~\cite{JFC},
abuses this standard and monitors the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
there are two main limitations compared with \tool: 
(1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen. The data can only be collected by \ac{JFA} after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections. For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
(2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}. \tool attacks the victim's device over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connectors including MicroUSB~\cite{li2018usb}. So \tool has a wider attack range.
